---
title: "Untitled"
author: ""
date: ""
output: 
  html_document:
    fig_height: 3
    fig_width: 5
  pdf_document:
    fig_height: 3
    fig_width: 5
  word_document:
    fig_height: 3
    fig_width: 5
---

```{r, setup, include=FALSE}
require(mosaic)   # Load additional packages here 
knitr::opts_chunk$set(
  tidy=FALSE,     # display code as typed
  size="small")   # slightly smaller font for code
```


Delete this sentence and enter your text here.

```{r}
require(imager)
require(abind)
require(plotly)
library(rgl)

Lighthouse<-load.image("Nationaly_Theatre.jpg")

dim(Lighthouse)


```


```{r}
Lighthouse<-load.image("lighthouse.jpg")
col3<-load.image("3col.jpg")

dim(Lighthouse)

#grab color matrices
red = Lighthouse[,,,1]
green = Lighthouse[,,,2]
blue = Lighthouse[,,,3]

dim(blue)


#second image color matrices
red1=col3[,,1]
green3=col3[,,3]
blue2=col3[,,2]


R=red[,1]
G=green[,1]
B=blue[,1]

as.list(R)

rgbdf<-data.frame(R=as.numeric(red),G=as.numeric(green),B=as.numeric(blue))
dim(rgbdf)

print(rgbdf)

```


```{r}
plot(Lighthouse)
plot(col3)

#3d plot of Lighthouse image colors
plot_ly(x = rgbdf$R, y = rgbdf$G, z = rgbdf$B, size=1)

#3d plot of 3col image colors
plot_ly(x = jitter(red1[,1], 5),y = jitter(green3[,1],5), z = jitter(blue2[,1], 5), size=1)
```


```{r}



#K cluster
clusters=kmeans(rgbdf, 4, iter.max=200)

#Turn the k clusters into a factor variable
rgbdf$clust <- factor(clusters$cluster)

(clusters$cluster)

#Plot of Cluster centers
plot_ly(x = jitter(clusters$centers[,1], 1),y = jitter(clusters$centers[,2], 1), z = jitter(clusters$centers[,3],1), size=1)



#Hexcodes for cluster centers
colors=rgb(red=clusters$centers[,1] ,green=clusters$centers[,2], blue=clusters$centers[,3]  , maxColorValue=1)

plot_ly(x = rgbdf$R, y = rgbdf$G, z = rgbdf$B, size=1, color=rgbdf$clust, colors=c("#366186", "#AEC6E2", "#98BEE7", "#BDC4CE", "#776760", "#ACB4BF", "#A6958A", "#70A6DA", "#F2E6DC", "#9EBBDB", "#ABBED6","#216C9D", "#07517D", "#8DB9E6", "#F2544E" ,"#B7BCC4", "#B3A195", "#BAC1CA", "#B8C7D9", "#A3C3E6", "#156393", "#3477A8","#3C342B", "#0C5A89", "#9B8B80", "#82B3E5", "#C3B2A7" ,"#AFBCCC", "#BBC5D1", "#8E8178", "#B1050C"))

```



```{r}
S<-matrix(unlist(clusters$cluster), ncol = 360, byrow = FALSE)

dim(S)
dim(Lighthouse)[2]

clusters$centers[,1][1]


PaintByNumber <-function(x, k){
  red = x[,,,1]
  green = x[,,,2]
  blue = x[,,,3]
  
  rgbdf<-data.frame(R=as.numeric(red),G=as.numeric(green),B=as.numeric(blue))
  clusters=kmeans(rgbdf, k, iter.max=250)
  rgbdf$clust <- factor(clusters$cluster)
  
  PixCol<-matrix(unlist(clusters$cluster), ncol = dim(x)[2], byrow = FALSE)
  return(list("Map"=PixCol, "Centers"=clusters$centers))
  
}



ColReplace <- function(x, y, k){
  
   #RED
  redmat <-x
  
  for (t in 1:k){
    redmat[redmat == t] <- y[t,1]
  }
  
  #Green
  greenmat <-x
  
  for (t in 1:k){
    greenmat[greenmat == t] <- y[t,2]
  }
  
  #BLUE
  bluemat <-x
  
  for (t in 1:k){
    bluemat[bluemat == t] <- y[t,3]
  }
  
  
  
  
  CompMat<-abind(redmat,greenmat,bluemat, rev.along=0)
  
  return(CompMat)
  
  
}


TRY1=ColReplace(S,clusters$centers,4)

dim(TRY1)



plot(as.cimg(TRY1), axes = FALSE)

Brut<-load.image("Nationaly_Theatre.jpg")
Frst<-load.image("forest.jpg")


BrutPixCol<-PaintByNumber(Brut, 3)
BrutPoster<-ColReplace(BrutPixCol$Map,BrutPixCol$Centers , 3)

plot(as.cimg(BrutPoster))

FrstPixCol<-PaintByNumber(Frst, 3)
FrstPoster<-ColReplace(FrstPixCol$Map,FrstPixCol$Centers , 3)

plot(as.cimg(FrstPoster))




